Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-25 paper/paper.tex
#27 expand data section

@@

I code such an "event" variable as missing for periods that are earlier than the first recorded event or later than the last
recorded event in a city.

Since I use some subset of construction as the outcome variable in all regressions, it is necessary to drop missing values.

@@

@@

The raw \textit{Territorial Histories} dataset starts out with 1,471,934 yearly observations. Two observations per city --- the first and the last year --- are lost while coding switches, for a total of 4,780. The remaining 1,467,154 yearly observations are aggregated into 30,980 observations with 50-year spacing. Of these I drop 16,110 that are not covered by the construction data. Finally, the baseline versions of all specifications in this paper restrict the sample to cities with no more than two lifetime switches. This will remove another 9,975 observations, leaving 6,635 in the baseline sample.

>>>>

A city-by-year panel of territorial history, taken from \cite{pt2}, forms the backbone of my dataset. For each city in each year it identifies the noble lineage to whose territory the city belonged in that year. This is what I

@@

Different types of construction

Additionally, conflict

Since I use some subset of construction as the outcome variable in all regressions, it is necessary to drop missing values. I code "event" variables as missing for periods that are earlier than the first recorded event or later than the last recorded event in a city.

@@

The aggregated indicators for construction and conflict take the value 1 if at least one event was recorded during the period. The switches and rule types

@@

The raw \textit{Territorial Histories} dataset starts out with 1,471,934 yearly observations. I lose two observations per city --- the first and the last year --- while coding switches, for a total of 4,780. I aggregate the remaining 1,467,154 yearly observations into 30,980 observations with 50-year spacing. Of these I drop 16,110 that are not covered by the construction data. Finally, the baseline versions of all specifications in this paper restrict the sample to cities with no more than two lifetime switches. This will remove another 9,975 observations, leaving 6,635 in the baseline sample.
